Transparency of COVID-19-related research - Analysis

### 2022-04-27 rmarkdown-covid-19-transparent-analysis.Rmd
First draft

```{r}
pacman::p_load(tidyverse,
               lubridate, 
               here, 
               ggplot2,
               knitr,
               here,
               epiR,
               ggpubr,
               tibble)
```

@@

# Results
Number of all papers (open access and non open access), open-access papers and open-access percentage:
```{r}
kable(data.frame(hits_all = 175550, 
           hits_oa = 133470,
           oa_percentage = round((133470/175550)*100, 1)))
```

Undownloadable papers:
```{r}
c(number = 133470 - nrow(opendata), 
  percentage = round((133470 - nrow(opendata))/133470*100, 1))
```

@@

The number of journals in our dataset:
```{r}
length(table(opendata$journal))
```
Top 10 journals with the highest number of articles in our dataset, from high to low:
```{r}
kable(head(table(opendata$journal) 
           %>% as.data.frame() 
           %>% arrange(desc(Freq)), 10))
```

@@

```{r}
opendata %>% 
        mutate(journal = fct_lump_prop(journal, prop = 0.01) ) %>% 
        count(journal) %>% 
        arrange(desc(n)) %>% 
        knitr::kable()
```

@@

Characteristics of the paper with the highest number of citations:
```{r}
kable(opendata[which.max(opendata$citedByCount),] %>% 
  select(citedByCount, pmid, pmcid, doi.x, title, authorString, journalTitle, pubYear))
```

@@

Confidence interval for CoI:
```{r}
library(epiR)

@@

## Journal Impact Factor (JIF) analyses

First, importing jif file:
```{r}
jif <- read.csv(here("data", "jif_2020.csv"))
```

Merging it with opendata:
```{r}
db_jif <- merge(opendata, jif, by.x = "journalIssn", by.y = "ISSN")
db_jif$X2020.JIF <- as.numeric(db_jif$X2020.JIF)
```

Total number of papers published in journals with a JIF:
```{r}
nrow(db_jif)
```

JIF based on COI disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_coi_pred) %>% 
  summarise(Median = round(median(X2020.JIF, na.rm = T), 1),
            IQR = round(IQR(X2020.JIF, na.rm = T), 2)))

Citation based on COI disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_coi_pred) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

Test for normality:
```{r}
set.seed(10)

with(db_jif, shapiro.test(sample(X2020.JIF[is_coi_pred == TRUE], 5000)))
with(db_jif, shapiro.test(X2020.JIF[is_coi_pred == FALSE]))

with(db_jif, shapiro.test(sample(citedByCount[is_coi_pred == TRUE], 5000)))
with(db_jif, shapiro.test(citedByCount[is_coi_pred == FALSE]))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_coi_pred, data = db_jif, exact = FALSE)

wilcox.test(citedByCount~is_coi_pred, data = db_jif, exact = FALSE)
```

JIF based on funding disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_fund_pred) %>% 
  summarise(Median = round(median(X2020.JIF, na.rm = T), 1),
            IQR = round(IQR(X2020.JIF, na.rm = T), 2)))

Citation based on funding disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_fund_pred) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

Test for normality:
```{r}
set.seed(10)

with(db_jif, shapiro.test(sample(X2020.JIF[is_fund_pred == TRUE], 5000)))
with(db_jif, shapiro.test(sample(X2020.JIF[is_fund_pred == FALSE], 5000)))

with(db_jif, shapiro.test(sample(citedByCount[is_fund_pred == TRUE], 5000)))
with(db_jif, shapiro.test(sample(citedByCount[is_fund_pred == FALSE], 5000)))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_fund_pred, data = db_jif, exact = FALSE)

wilcox.test(citedByCount~is_fund_pred, data = db_jif, exact = FALSE)
```

JIF based on registration:
```{r}
kable(db_jif %>% 
  group_by(is_register_pred) %>% 
  summarise(Median = round(median(X2020.JIF, na.rm = T), 1),
            IQR = round(IQR(X2020.JIF, na.rm = T), 2)))

Citation based on funding disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_register_pred) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

Test for normality:
```{r}
set.seed(10)

with(db_jif, shapiro.test(X2020.JIF[is_register_pred == TRUE]))
with(db_jif, shapiro.test(sample(X2020.JIF[is_register_pred == FALSE], 5000)))

with(db_jif, shapiro.test(citedByCount[is_register_pred == TRUE]))
with(db_jif, shapiro.test(sample(citedByCount[is_register_pred == FALSE], 5000)))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_register_pred, data = db_jif, exact = FALSE)

wilcox.test(citedByCount~is_register_pred, data = db_jif, exact = FALSE)
```

JIF based on data sharing:
```{r}
kable(db_jif %>% 
  group_by(is_open_data) %>% 
  summarise(Median = round(median(X2020.JIF, na.rm = T), 1),
            IQR = round(IQR(X2020.JIF, na.rm = T), 2)))

Citation based on funding disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_open_data) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

Test for normality:
```{r}
set.seed(10)

with(db_jif, shapiro.test(sample(X2020.JIF[is_open_data == TRUE], 5000)))
with(db_jif, shapiro.test(sample(X2020.JIF[is_open_data == FALSE], 5000)))

with(db_jif, shapiro.test(sample(citedByCount[is_open_data == TRUE], 5000)))
with(db_jif, shapiro.test(sample(citedByCount[is_open_data == FALSE], 5000)))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_open_data, data = db_jif, exact = FALSE)

wilcox.test(citedByCount~is_open_data, data = db_jif, exact = FALSE)
```

JIF based on code sharing:
```{r}
kable(db_jif %>% 
  group_by(is_open_code) %>% 
  summarise(Median = round(median(X2020.JIF, na.rm = T), 1),
            IQR = round(IQR(X2020.JIF, na.rm = T), 2)))

Citation based on funding disclosure:
```{r}
kable(db_jif %>% 
  group_by(is_open_code) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

Test for normality:
```{r}
set.seed(10)

with(db_jif, shapiro.test(X2020.JIF[is_open_code == TRUE]))
with(db_jif, shapiro.test(sample(X2020.JIF[is_open_code == FALSE], 5000)))

with(db_jif, shapiro.test(citedByCount[is_open_code == TRUE]))
with(db_jif, shapiro.test(sample(citedByCount[is_open_code == FALSE], 5000)))
```

Data is not normal, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(X2020.JIF~is_open_code, data = db_jif, exact = FALSE)

wilcox.test(citedByCount~is_open_code, data = db_jif, exact = FALSE)
```

## Sum of five indicators
```{r}
opendata <- opendata %>% mutate(sumOfIndicators = rowSums(opendata %>% select(is_coi_pred, is_register_pred, is_fund_pred, is_open_data, is_open_code)))
```

Number of papers with each number of TRUE indicators:
```{r}
c(five_ind = nrow(filter(opendata, sumOfIndicators == 5)),
  four_ind = nrow(filter(opendata, sumOfIndicators == 4)),
  three_ind = nrow(filter(opendata, sumOfIndicators == 3)),
  two_ind = nrow(filter(opendata, sumOfIndicators == 2)),
  one_ind = nrow(filter(opendata, sumOfIndicators == 1)),
  zero_ind = nrow(filter(opendata, sumOfIndicators == 0)))
```

Percentage of papers with each number of TRUE indicators:
```{r}

c(five_ind = round(nrow(filter(opendata, sumOfIndicators == 5))/nrow(opendata)*100, 1),
  four_ind = round(nrow(filter(opendata, sumOfIndicators == 4))/nrow(opendata)*100, 1),
  three_ind = round(nrow(filter(opendata, sumOfIndicators == 3))/nrow(opendata)*100, 1),
  two_ind = round(nrow(filter(opendata, sumOfIndicators == 2))/nrow(opendata)*100, 1),
  one_ind = round(nrow(filter(opendata, sumOfIndicators == 1))/nrow(opendata)*100, 1),
  zero_ind = round(nrow(filter(opendata, sumOfIndicators == 0))/nrow(opendata)*100, 1))
```

To know which of the indicators were TRUE in papers with two TRUE indicators:
```{r}

nrow_ <- nrow(filter(opendata, sumOfIndicators == 2))

c(coi = round(nrow(filter(opendata, sumOfIndicators == 2 & is_coi_pred))/nrow_*100, 1),
  fund = round(nrow(filter(opendata, sumOfIndicators == 2 & is_fund_pred))/nrow_*100, 1),
  reg = round(nrow(filter(opendata, sumOfIndicators == 2 & is_register_pred))/nrow_*100, 1),
  data = round(nrow(filter(opendata, sumOfIndicators == 2 & is_open_data))/nrow_*100, 1),
  code = round(nrow(filter(opendata, sumOfIndicators == 2 & is_open_code))/nrow_*100, 1))
```

## Monthly trend
Figure 1:
```{r}
library(tibble)

@@

```{r}
library(ggpubr)

@@

>>>>

```{r}
pacman::p_load(dplyr,
               ggplot2,
               knitr,
               here,
               tidyr,
               europepmc,
               lubridate,
               ggpubr,
               epiR,
               gtsummary,
               forcats,
               nortest,
               caret,
               tibble)
```

@@

# Results
Number of all papers (open access and non open access), open-access papers and open-access percentage:
```{r}
kable(data.frame(hits_all = 175544, 
           hits_oa = 133467,
           oa_percentage = round((133467/175544)*100, 1)))
```

Undownloadable papers:
```{r}
c(number = 133467 - nrow(opendata), 
  percentage = round((133467 - nrow(opendata))/133467*100, 1))
```

@@

The number of journals in our dataset:
```{r}
length(table(opendata$journalTitle))
```
Top 10 journals with the highest number of articles in our dataset, from high to low:
```{r}
kable(head(table(opendata$journalTitle) 
           %>% as.data.frame() 
           %>% arrange(desc(Freq)), 10))
```

@@

```{r}
opendata %>% 
        mutate(journal = fct_lump_prop(journalTitle, prop = 0.01) ) %>% 
        count(journal) %>% 
        arrange(desc(n)) %>% 
        knitr::kable()
```

@@

Characteristics of the paper with the highest number of citations:
```{r}
kable(opendata[which.max(opendata$citedByCount),] %>% 
  select(citedByCount, pmid, pmcid, doi, title, authorString, journalTitle, year_firstpub))
```

@@

Confidence interval for CoI:
```{r}

@@

Sum of five indicators:
```{r}
opendata %>% mutate(sum = rowSums(opendata %>% select(is_coi_pred, is_register_pred, is_fund_pred, is_open_data, is_open_code))) %>% select(sum) %>% tbl_summary()
```

## Journal-related differences in transparency (Table 1)

Total number of papers published in journals with a JIF:
```{r}
table(is.na(opendata$jif2020))
```

Five highest impact journals
```{r}

tapply(opendata$jif2020, opendata$journalTitle, max) %>% as.data.frame() %>% arrange(desc(.)) %>% head(5)

opendata$jif2020c = ifelse(opendata$jif2020 < 79.321,"Other", opendata$journalTitle)
```

Table 1A
```{r}
set.seed(100)
opendata %>% 
  select(journalTitle,is_coi_pred,is_fund_pred,is_register_pred,is_open_data,is_open_code) %>%
        mutate(journalTitle = fct_lump(journalTitle,n=5)) %>%
  tbl_summary(by=journalTitle, percent="column",
              label = c(is_coi_pred ~ "COI disclosure", is_fund_pred ~ "Funding disclosure", is_register_pred ~ "Protocol registration", is_open_data ~ "Data sharing", is_open_code ~ "Code sharing")) %>%
  add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE)) %>%
        as_flex_table()
```

Table 1B
```{r}
set.seed(100)
opendata %>% 
  select(jif2020c,is_coi_pred,is_fund_pred,is_register_pred,is_open_data,is_open_code) %>%
  tbl_summary(by=jif2020c, percent="column",
              label = c(is_coi_pred ~ "COI disclosure", is_fund_pred ~ "Funding disclosure", is_register_pred ~ "Protocol registration", is_open_data ~ "Data sharing", is_open_code ~ "Code sharing")) %>%
  add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE)) %>%
        as_flex_table()
```

## Publisher-related differences in transparency (Table 2)

Table 2
```{r}
set.seed(100)
opendata %>% 
  select(scimago_publisher,is_coi_pred,is_fund_pred,is_register_pred,is_open_data,is_open_code) %>%
        mutate(scimago_publisher = fct_lump(scimago_publisher,n=6)) %>%
  tbl_summary(by=scimago_publisher, percent="column",
              label = c(is_coi_pred ~ "COI disclosure", is_fund_pred ~ "Funding disclosure", is_register_pred ~ "Protocol registration", is_open_data ~ "Data sharing", is_open_code ~ "Code sharing")) %>%
  add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE)) %>%
        as_flex_table()
```

## Journal Impact Factor (JIF) and citation count analyses (Table 3)

Total number of papers published in journals with no JIF:
```{r}
sum(is.na(opendata$jif2020))
```
Normality of JIFs and citations
```{r}
hist(opendata$jif2020)
hist(opendata$citedByCount)
ad.test(opendata$jif2020)
ad.test(opendata$citedByCount)
```

JIF and citations based on COI disclosure:
```{r}
kable(opendata %>% 
  group_by(is_coi_pred) %>% 
  summarise(Median = round(median(jif2020, na.rm = T), 1),
            IQR = round(IQR(jif2020, na.rm = T), 2)))

kable(opendata %>% 
  group_by(is_coi_pred) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

Data was not normally distributed, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(jif2020~is_coi_pred, data = opendata, exact = FALSE)
wilcox.test(citedByCount~is_coi_pred, data = opendata, exact = FALSE)
```

JIF and citations based on funding disclosure:
```{r}
kable(opendata %>% 
  group_by(is_fund_pred) %>% 
  summarise(Median = round(median(jif2020, na.rm = T), 1),
            IQR = round(IQR(jif2020, na.rm = T), 2)))

kable(opendata %>% 
  group_by(is_fund_pred) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

Data was not normally distributed, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(jif2020~is_fund_pred, data = opendata, exact = FALSE)
wilcox.test(citedByCount~is_fund_pred, data = opendata, exact = FALSE)
```

JIF and citations based on registration:
```{r}
kable(opendata %>% 
  group_by(is_register_pred) %>% 
  summarise(Median = round(median(jif2020, na.rm = T), 1),
            IQR = round(IQR(jif2020, na.rm = T), 2)))

kable(opendata %>% 
  group_by(is_register_pred) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

Data was not normally distributed, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(jif2020~is_register_pred, data = opendata, exact = FALSE)
wilcox.test(citedByCount~is_register_pred, data = opendata, exact = FALSE)
```

JIF and citations based on data sharing:
```{r}
kable(opendata %>% 
  group_by(is_open_data) %>% 
  summarise(Median = round(median(jif2020, na.rm = T), 1),
            IQR = round(IQR(jif2020, na.rm = T), 2)))

kable(opendata %>% 
  group_by(is_open_data) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

Data was not normally distributed, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(jif2020~is_open_data, data = opendata, exact = FALSE)
wilcox.test(citedByCount~is_open_data, data = opendata, exact = FALSE)
```

JIF and citations based on code sharing:
```{r}
kable(opendata %>% 
  group_by(is_open_code) %>% 
  summarise(Median = round(median(jif2020, na.rm = T), 1),
            IQR = round(IQR(jif2020, na.rm = T), 2)))

kable(opendata %>% 
  group_by(is_open_code) %>% 
  summarise(Median = round(median(citedByCount, na.rm = T), 1),
            IQR = round(IQR(citedByCount, na.rm = T), 2)))
```

Data was not normally distributed, hence we will use unpaired two-samples Wilcoxon test.
```{r}
wilcox.test(jif2020~is_open_code, data = opendata, exact = FALSE)
wilcox.test(citedByCount~is_open_code, data = opendata, exact = FALSE)
```

## Monthly trend
Figure 1:
```{r}

@@

```{r}

@@

# Appendix
## Journals

Total number of papers published in journals with an SJR:
```{r}
table(is.na(opendata$sjr2020))
```

Top five journals in SJR:
```{r}
tapply(opendata$sjr2020, opendata$journalTitle, max) %>% as.data.frame() %>% arrange(desc(.)) %>% head(5)

opendata$sjr2020c = ifelse(opendata$sjr2020 < 26.304,"Other", opendata$journalTitle)
```

Table S1
```{r}
set.seed(100)
opendata %>% 
  select(sjr2020c,is_coi_pred,is_fund_pred,is_register_pred,is_open_data,is_open_code) %>%
  tbl_summary(by=sjr2020c, percent="column",
              label = c(is_coi_pred ~ "COI disclosure", is_fund_pred ~ "Funding disclosure", is_register_pred ~ "Protocol registration", is_open_data ~ "Data sharing", is_open_code ~ "Code sharing")) %>%
  add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE)) %>%
        as_flex_table()
```

Top five journals in H-index:
```{r}
tapply(opendata$scimago_hindex, opendata$journalTitle, max) %>% as.data.frame() %>% arrange(desc(.)) %>% head(5)

opendata$hindexc = ifelse(opendata$scimago_hindex < 771,"Other", opendata$journalTitle)
```

Table S2
```{r}
set.seed(100)
opendata %>% 
  select(hindexc,is_coi_pred,is_fund_pred,is_register_pred,is_open_data,is_open_code) %>%
  tbl_summary(by=hindexc, percent="column",
              label = c(is_coi_pred ~ "COI disclosure", is_fund_pred ~ "Funding disclosure", is_register_pred ~ "Protocol registration", is_open_data ~ "Data sharing", is_open_code ~ "Code sharing")) %>%
  add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE)) %>%
        as_flex_table()
```

## Appendix 3:
Correct p-values (considering all levels)
```{r}
opendata %>% 
  select(journalTitle,is_coi_pred) %>%
        table() %>%
        fisher.test(simulate.p.value=TRUE)
opendata %>% 
  select(journalTitle,is_fund_pred) %>%
        table() %>%
        fisher.test(simulate.p.value=TRUE)
opendata %>% 
  select(journalTitle,is_register_pred) %>%
        table() %>%
        fisher.test(simulate.p.value=TRUE)
opendata %>% 
  select(journalTitle,is_open_data) %>%
        table() %>%
        fisher.test(simulate.p.value=TRUE)
opendata %>% 
  select(journalTitle,is_open_code) %>%
        table() %>%
        fisher.test(simulate.p.value=TRUE)
```

Code sharing for all journals
```{r}
set.seed(100)
opendata %>% 
  select(journalTitle,is_open_code) %>%
  tbl_summary(by=is_open_code, percent="row", sort = list(everything() ~ "frequency"))%>%
  add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE)) %>% 
        as_flex_table()
```

Data sharing for all journals
```{r}
set.seed(100)
opendata %>% 
  select(journalTitle,is_open_data) %>%
  tbl_summary(by=is_open_data, percent="row", sort = list(everything() ~ "frequency"))%>%
  add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE))%>% 
        as_flex_table()
```

Protocol registration for all journals
```{r}
set.seed(100)
opendata %>% 
  select(journalTitle,is_register_pred) %>%
  tbl_summary(by=is_register_pred, percent="row", sort = list(everything() ~ "frequency"))%>%
  add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE)) %>% 
        as_flex_table()
```

COI disclosure for all journals
```{r}
set.seed(100)
opendata %>% 
  select(journalTitle,is_coi_pred) %>%
  tbl_summary(by=is_coi_pred, percent="row", sort = list(everything() ~ "frequency"))%>%
  add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE))%>% 
        as_flex_table()
```

Funding disclosure for all journals
```{r}
set.seed(100)
opendata %>% 
  select(journalTitle,is_fund_pred) %>%
  tbl_summary(by=is_fund_pred, percent="row", sort = list(everything() ~ "frequency"))%>%
  add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE))%>% 
        as_flex_table()
```

# Publisher-related differences in transparency
Correct p-values (considering all levels)
```{r}
opendata %>% 
  select(scimago_publisher,is_coi_pred) %>%
        table() %>%
        fisher.test(simulate.p.value=TRUE)
opendata %>% 
  select(scimago_publisher,is_fund_pred) %>%
        table() %>%
        fisher.test(simulate.p.value=TRUE)
opendata %>% 
  select(scimago_publisher,is_register_pred) %>%
        table() %>%
        fisher.test(simulate.p.value=TRUE)
opendata %>% 
  select(scimago_publisher,is_open_data) %>%
        table() %>%
        fisher.test(simulate.p.value=TRUE)
opendata %>% 
  select(scimago_publisher,is_open_code) %>%
        table() %>%
        fisher.test(simulate.p.value=TRUE)
```

Data sharing for all publishers
```{r}
set.seed(100)
opendata %>% 
select(scimago_publisher,is_open_data) %>%
tbl_summary(by=is_open_data, percent="row", sort = list(everything() ~ "frequency"))%>%
 add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE))%>% 
        as_flex_table()
```

Protocol registeration in all publishers
```{r}
set.seed(100)
opendata %>% 
select(scimago_publisher,is_register_pred) %>%
tbl_summary(by=is_register_pred, percent="row", sort = list(everything() ~ "frequency"))%>%
  add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE))%>% 
        as_flex_table()
```

COI disclosure in all publishers
```{r}
set.seed(100)
opendata %>% 
select(scimago_publisher,is_coi_pred) %>%
tbl_summary(by=is_coi_pred, percent="row", sort = list(everything() ~ "frequency")) %>%
  add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE))%>% 
        as_flex_table()
```

Funding disclosure in all publishers
```{r}
set.seed(100)
opendata %>% 
select(scimago_publisher,is_fund_pred) %>%
tbl_summary(by=is_fund_pred, percent="row", sort = list(everything() ~ "frequency")) %>%
add_p(test.args=all_tests("fisher.test") ~ list(simulate.p.value=TRUE))%>% 
        as_flex_table()
```
